\documentclass[11pt]{report}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{times}

\begin{document}
\section*{Acknowledgments}
\label{sec:acknowledgments}

\paragraph*{Electricity systems.} We thank James Kelloway (National Grid ESO), Jack Kelly (Open Climate Fix), Zico Kolter (CMU), and Henry Richardson (WattTime) for their help and ideas in shaping this section. We also thank Samuel Buteau (Dalhousie University) and Marc Cormier (Dalhousie University) for their inputs on accelerated science and battery storage technologies; Julian Kates-Harbeck (Harvard) and Melrose Roderick (CMU) for their extensive inputs and ideas on nuclear fusion; and Alasdair Bruce (formerly National Grid ESO) for inputs on emissions factor forecasting and automated dispatch. Finally, we thank Lea Boche (EPRI), Carl Elkin (DeepMind), Jim Gao (DeepMind), Muhammad Hasan (DeepMind), Guannan He (CMU), Jeremy Keen (CMU), Zico Kolter (CMU), Luke Lavin (CMU), Sanam Mirzazad (EPRI), David Pfau (DeepMind), Crystal Qian (DeepMind), Juliet Rothenberg (DeepMind), Sims Witherspoon (DeepMind) and Matt Wytock (Gridmatic, Inc.) for helpful comments and feedback.

\paragraph*{Transportation.}
We are grateful for advice from Alan T.~Jenn (UC Davis) and Prithvi S.~Acharya (CMU) on electric vehicles, Alexandre Jacquillat (CMU) on decarbonizing aviation, Michael Whiston (CMU) on hydrogen fuel cells, Evan Sherwin (CMU) on alternative fuels, and Samuel Buteau (Dalhousie University) on batteries.

\paragraph*{Buildings and Cities.} We thank \'Erika Mata (IVL - Swedish Environmental Research Institute, IPCC Lead Author Buildings section), Duccio Piovani (nam.R) and Jack Kelly (Open Climate Fix) for feedback and ideas.

\paragraph*{Industry.}
We appreciate all the constructive feedback from Angela Acocella (MIT), Kevin McCloskey (Google), and Bill Tubbs (University of British Columbia), and we are grateful to Kipp Bradford (Yale) for his recommendations around embodied energy and refrigeration. Thanks to Allie Schwertner (Rockwell Automation), Greg Kochanski (Google), and Paul Weaver (Abstract) for their suggestions around optimizing industrial processes for low-carbon energy.

\paragraph*{Farms \& Forests.}
We would like to give thanks to David Marvin (Salo) and Remi Charpentier (Tesselo) on remote sensing for land use. Max Nova (SilviaTerra) provided insight on forestry, Mark Crowley (University of British Columbia) on forest fire management, Benjamin Deleener (ChrysaLabs) on precision agriculture, and Lindsay Brin (Element AI) on soil chemistry.

\paragraph{Climate prediction.} We thank Ghaleb Abdulla (LLNL), Ben Kravitz (PNNL) and David John Gagne II (UCAR) for enlightening conversations; Goodwin Gibbins (Imperial College London) and Ben Kravitz (PNNL) for detailed editing and feedback; and Claire Monteleoni (CU Boulder) and Prabhat (LBL) for feedback which improved the quality of this manuscript.

\paragraph*{Societal adaptation.}
We thank Loubna Benabbou (UQAR), Mike Sch{\"a}fer (University of Zurich), Andrea Garcia Tapia (Stevens Tech), Slava Jankin Mikhaylov (Hertie School Berlin), and Sarah M.~Fletcher (MIT) for valuable conversations on the social aspects of climate change. 

\paragraph*{Solar geoengineering.}
We thank David Keith (Harvard), Peter Irvine (Harvard), Zhen Dai (Harvard), Colleen Golja (Harvard), Ross Boczar (UC Berkeley), Jon Proctor (UC Berkeley), Ben Kravitz (Indiana University),  Andrew Lockley (University College London), Trude Storelvmo (University of Oslo), and Simon Gruber (University of Oslo) for help and useful feedback.

\paragraph*{Individual action.} We thank Priyanka deSouza (MIT), Olivier Corradi (Tomorrow), Jack Kelly (Open Climate Fix), Ioana Marinescu (UPenn), and Aven Satre-Meloy (Oxford).

\paragraph*{Collective Decisions.}
We thank Sebastian Sewerin (ETH Z\"urich), D.~Cale Reeves (UT Austin), and Rahul Ladhania (UPenn).

\paragraph*{Education.} We appreciated the constructive feedback received by Jacqueline Bourdeau (T\'{E}LUQ University), who gave us valuable insights regarding the field of AIED.

\paragraph*{Finance.} We thank Himanshu Gupta (ClimateAI), and Bjarne Steffen (ETH Z\"urich) for constructive discussions and the valuable feedback.

\paragraph*{}The authors gratefully acknowledge support from National Science Foundation grant 1803547, the Center for Climate and Energy Decision Making through a cooperative agreement between the National Science Foundation and Carnegie Mellon University (SES-00949710), US Department of Energy contract DE-FG02-97ER25308, the Natural Sciences and Engineering Research Council of Canada, and the MIT Media Lab Consortium.
\end{document}
